\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-11 paper.tex
rough work

@@

\author{\textbf{Matthew Doherty} \\ \textit{Rhodes University}} % Author and institution

@@

@@

Cryptostorm VPN connect over TLS 
192.36.27.5 -> Amsterdam IP for onion (Entry node)

@@

>>>>

\lstset{ 
%         language=Matlab,                                % choose the language of the code
%       basicstyle=10pt,                                % the size of the fonts that are used for the code
%         numbers=left,                                   % where to put the line-numbers
%         numberstyle=\footnotesize,                      % the size of the fonts that are used for the line-numbers
%         stepnumber=1,                                           % the step between two line-numbers. If it's 1 each line will be numbered
%         numbersep=5pt,                                  % how far the line-numbers are from the code
%       backgroundcolor=\color{white},          % choose the background color. You must add \usepackage{color}
%         showspaces=false,                               % show spaces adding particular underscores
%         showstringspaces=false,                         % underline spaces within strings
%         showtabs=false,                                         % show tabs within strings adding particular underscores
%       frame=single,                                           % adds a frame around the code
%       tabsize=2,                                              % sets default tabsize to 2 spaces
%       captionpos=b,                                           % sets the caption-position to bottom
         breaklines=true,                                        % sets automatic line breaking
%         breakatwhitespace=false,                        % sets if automatic breaks should only happen at whitespace
%         escapeinside={\%*}{*)}                          % if you want to add a comment within your code
}

@@

\author{\textbf{Matthew Doherty \& Daniel Delharpe} \\ \textit{Rhodes University}} % Author and institution

@@

A point to make about attacks of this kind, is that they can easily slip between the cracks since benign traffic is by far the most dominant communication on the network. Most of the traffic generated involves the target host receiving legitimate windows updates from trusted IP addresses. In monitoring the DNS traffic closely we found some interesting queries for known malicious sites. We set out to uncover when the infection shows and how communication with the C2 (command and control server) was carried out.

@@

Cryptostorm VPN connect over TLS 
192.36.27.5 -> Amsterdam IP for onion (Entry node)
103.198.0.2     45jngpxc4cgsxqxc.onion.link -> Singapore

@@

On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence. A mail with an attachment, potentially a msword document is fetched after a "503 Backend fetch failed". The destination IP is associated with a onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes before reaching the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those most vulnerable but also those who exploit it for profit. The ".link" allows for for convenience at the expense of \cite{onionlink}. This allowed the target system to visit a TOR hidden service hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of an malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}.

\begin{lstlisting}
2017-03-20 15:20:08.517517 IP (tos 0x0, ttl 128, id 4560, offset 0, flags [DF], proto TCP (6), length 551)
    10.0.0.5.52848 > 103.198.0.2.80: Flags [P.], cksum 0x4696 (correct), seq 1:512, ack 1, win 4236, length 511: HTTP, length: 511
        GET / HTTP/1.1
        Accept: image/jpeg, application/x-ms-application, image/gif, application/xaml+xml, image/pjpeg, application/x-ms-xbap, application/vnd.ms-excel, application/vnd.ms-powerpoint, application/msword, */*
        Accept-Language: en-US
        User-Agent: Mozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)
        Accept-Encoding: gzip, deflate
        Host: 45jngpxc4cgsxqxc.onion.link
        Connection: Keep-Alive

E..'..@...u4
...g....p.P*R>....*P...F...GET / HTTP/1.1
Accept: image/jpeg, application/x-ms-application, image/gif, application/xaml+xml, image/pjpeg, application/x-ms-xbap, application/vnd.ms-excel, application/vnd.ms-powerpoint, application/msword, */*
Accept-Language: en-US
User-Agent: Mozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)
Accept-Encoding: gzip, deflate
Host: 45jngpxc4cgsxqxc.onion.link
Connection: Keep-Alive

2017-03-20 15:20:08.790039 IP (tos 0x18, ttl 52, id 30272, offset 0, flags [DF], proto TCP (6), length 524)
    103.198.0.2.80 > 10.0.0.5.52848: Flags [P.], cksum 0x6305 (correct), seq 1:485, ack 512, win 123, length 484: HTTP, length: 484
        HTTP/1.1 503 Backend fetch failed
        Date: Mon, 20 Mar 2017 08:21:16 GMT
        Content-Type: text/html; charset=utf-8
        Retry-After: 5
        Age: 0
        X-Cache: MISS
        Content-Length: 286
        Connection: keep-alive

        <!DOCTYPE html>
        <html>
          <head>
            <title>503 Backend fetch failed</title>
          </head>
          <body>
            <h1>Error 503 Backend fetch failed</h1>
            <p>Backend fetch failed</p>
            <h3>Guru Meditation:</h3>
            <p>XID: 288687254</p>
            <hr>
            <p>Varnish cache server</p>
          </body>
        </html>
    103.198.0.2.80 > 10.0.0.5.52849: Flags [P.], cksum 0x7d3d (correct), seq 1:1133, ack 311, win 123, length 1132: HTTP, length: 1132
        HTTP/1.1 500 Internal Server Error
        Content-Length: 856
        Content-Encoding: gzip
        X-Check-Tor: false
        Content-Security-Policy: upgrade-insecure-requests
        X-Onion-Url: 45jngpxc4cgsxqxc.onion
        Date: Mon, 20 Mar 2017 08:21:20 GMT
        Age: 0
        X-Cache: MISS
        Connection: keep-alive

E.....@.4..zg...
....P.q!'(.k.k}P..{}=..HTTP/1.1 500 Internal Server Error
Content-Length: 856
Content-Encoding: gzip
X-Check-Tor: false
Content-Security-Policy: upgrade-insecure-requests
X-Onion-Url: 45jngpxc4cgsxqxc.onion
Date: Mon, 20 Mar 2017 08:21:20 GMT
Age: 0
X-Cache: MISS
Connection: keep-alive

...........U[o.6.~v~....{.........@...k2.1..c..E2$....!\%........|.....Y.[Y\..5......^Bq..V.B=..Rw."J{Rj....k2..Q.....v..}..`............9...,<.(.n.........{..s'.9...?........6.....E;...`O..-........(.4..9el.....p.\.2.9-...n.... s..A.k.|.8.\i....2....3.7|..Z.....-u....+.6.....N?...M.
.n.-2..+.2..*dm......[RJ.\N.B
.Yn.X...D..h......E...-S.jJ..............g...Y.....pb......+....*..k..../I....Q7x.....r\%....NT...l:=.}2..r..[p....5...........?....W..Z....B2.....H..(._JQ>.t...O..s..7..]P"*,.~.....+x{ .~..X..E.k.......S3.........7(LK.wB.D..\..0G.$.2..B.......,...'y.......,H...   .{.|.a....)Tz.^.,.;N<.F[..iDYv...U<hK....Og....3f.oFi....>.
.1{.$.W....CI..bmqJ......2c...S...1...O.._xk......J.......;'.E_qs...../.....S.!...}.}.N!I....c..V..c..o\%.2.R.....D...l...0..m....?.....?}K.X.........ry?`~...........xl...-.....c.:yN   ~......n.36z..n.#|..qn..M..w..t.......

    10.0.0.5.137 > 103.198.0.2.137: [udp sum ok]
>>> NBT UDP PACKET(137): QUERY; REQUEST; BROADCAST
TrnID=0xF66C
OpCode=0
NmFlags=0x1
Rcode=0
QueryCount=1
AnswerCount=0
AuthorityCount=0
AddressRecCount=0
QuestionRecords:
Name=*               NameType=0x00 (Workstation)
QuestionType=0x21
QuestionClass=0x1
\end{lstlisting}
\begin{lstlisting}
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52849         -> 103.198.0.2:80         [http] Request { method: "GET", uri: "/favicon.ico", version: "1.1", host: Some("45jngpxc4cgsxqxc.onion.link"), agent
: Some("Mozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)"), referer: None, auth: None, cookies: N
one }
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61226         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.198.103.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61226         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:51704         -> 10.0.0.2:53            [dns] req, (A, "45jngpxc4cgsxqxc.torstorm.org")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:51704         [dns] resp, ("45jngpxc4cgsxqxc.torstorm.org", A(94.242.58.199))
                                                                                                           ("45jngpxc4cgsxqxc.torstorm.org", A(192.64.119.254))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49695         -> 10.0.0.2:53            [dns] req, (AAAA, "45jngpxc4cgsxqxc.torstorm.org")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49695         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:57862         -> 10.0.0.2:53            [dns] req, (PTR, "199.58.242.94.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:57862         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52851         -> 192.64.119.254:80      [http] Request { method: "GET", uri: "/", version: "1.1", host: Some("45jngpxc4cgsxqxc.torstorm.org"), agent: Some("M
ozilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)"), referer: None, auth: None, cookies: None }
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [tcp] 192.64.119.254:80      -> 10.0.0.5:52851         [text] "HTTP/1.1 302 Found\r\nServer: nginx\r\nDate: Mon, 20 Mar 2017 13:20:33 GMT\r\nContent-Type: text/html; charse
t=utf-8\r\nContent-Length: 45\r\nConnection: keep-alive\r\nLocation: https://cryptostorm.is\r\nX-Served-By: Namecheap URL Forward\r\n\r\n<a href=\"https://cryptostorm.is\">Found</a>.\n\n"
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:50923         -> 10.0.0.2:53            [dns] req, (A, "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:50923         [dns] resp, ("cryptostorm.is", A(46.165.240.186))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52680         -> 10.0.0.2:53            [dns] req, (AAAA, "cryptostorm.is")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52680         -> 10.0.0.2:53            [dns] req, (AAAA, "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52680         -> 10.0.0.2:53            [dns] req, (AAAA, "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52680         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52680         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52680         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:60307         -> 10.0.0.2:53            [dns] req, (PTR, "254.119.64.192.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52852         -> 46.165.240.186:443     [tls] ClientHello (hostname: "cryptostorm.is")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:60307         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:61872         -> 10.0.0.2:53            [dns] req, (PTR, "186.240.165.46.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:61872         [dns] resp, ("186.240.165.46.in-addr.arpa", PTR("cryptostorm.is"))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:59404         -> 10.0.0.2:53            [dns] req, (A, "ocsp.comodoca.com")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:59404         [dns] resp, ("ocsp.comodoca.com", A(178.255.83.1))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:64237         -> 10.0.0.2:53            [dns] req, (AAAA, "ocsp.comodoca.com")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:64237         [dns] resp, ("ocsp.comodoca.com", AAAA(2a02:1788:2fd::b2ff:5301))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:64237         -> 10.0.0.2:53            [dns] req, (AAAA, "ocsp.comodoca.com")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:64237         [dns] resp, ("ocsp.comodoca.com", AAAA(2a02:1788:2fd::b2ff:5301))
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52853         -> 178.255.83.1:80        [http] Request { method: "GET", uri: "/MFEwTzBNMEswSTAJBgUrDgMCGgUABBReAhtobFzTvhaRmVeJ38QUchY9AwQUu69\%2BAj36pvE8hI6t
7jiY7NkyMtQCECsuburZdTZsFIpu26N8jAc\%3D", version: "1.1", host: Some("ocsp.comodoca.com"), agent: Some("Microsoft-CryptoAPI/6.1"), referer: None, auth: None, cookies: None }
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:54122         -> 10.0.0.2:53            [dns] req, (PTR, "1.83.255.178.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:54122         [dns] resp, ("1.83.255.178.in-addr.arpa", PTR("ocsp.comodoca.com"))
\end{lstlisting}
\begin{lstlisting}
Put your code here.
\end{lstlisting}
\begin{lstlisting}
Put your code here.
\end{lstlisting}

Following execution of the payload we can infer that the DNS quieries were made in order to resolve another .onion domain.

\begin{lstlisting}
("45jngpxc4cgsxqxc.torstorm.org", A(94.242.58.199))
\end{lstlisting}

Next we see a query for the domain cyrptostorm.is. Cryptostorm is a German based VPN service that markets itself as for the "truly paranoid" \cite{cryptostorm}. The malware then follows to make HTTP get requests with encoded URLs to a Beijing IP. This could possibly be the keys generated for the encryption based on the user agent of Mircrosoft-CryptoAPI/6.1, Microsoft's Cyrptographic Application programming interface. After this phase an TLS connection is established with the Cryptostorm using openVPN. This takes place as the user casually visits googlecode.com and stripe.com.

\begin{lstlisting}
("186.240.165.46.in-addr.arpa", PTR("cryptostorm.is"))
\end{lstlisting}

\begin{lstlisting}
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52853         -> 178.255.83.1:80        [http] Request { method: "GET", uri: "/MFEwTzBNMEswSTAJBgUrDgMCGgUABBReAhtobFzTvhaRmVeJ38QUchY9AwQUu69\%2BAj36pvE8hI6t
7jiY7NkyMtQCECsuburZdTZsFIpu26N8jAc\%3D", version: "1.1", host: Some("ocsp.comodoca.com"), agent: Some("Microsoft-CryptoAPI/6.1"), referer: None, auth: None, cookies: None }

00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:52856         -> 197.84.135.45:80       [http] Request { method: "GET", uri: "/ocsp/MEkwRzBFMEMwQTAJBgUrDgMCGgUABBTy4Gr5hYodjXCbSRkjeqm1Gih\%2BZAQUSt0GFhu89mi
1dvWBtrtiGrpagS8CCBmQZHv1CkD2", version: "1.1", host: Some("clients1.google.com"), agent: Some("Microsoft-CryptoAPI/6.1"), referer: None, auth: None, cookies: None }
\end{lstlisting}

The target host ceases to exist on the networking failing to respond to even ARP broadcasts from this point fordard.

\begin{lstlisting}
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "255.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "252.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "5.0.0.10.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "252.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.0.10.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52394         -> 10.0.0.2:53            [dns] req, (PTR, "5.7.a.9.c.3.8.2.0.0.c.0.a.f.1.8.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52394         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:53658         -> 10.0.0.2:53            [dns] req, (PTR, "255.0.0.10.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:53658         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:59669         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:51331         -> 10.0.0.2:53            [dns] req, (PTR, "2.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:59669         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:55984         -> 10.0.0.2:53            [dns] req, (PTR, "3.0.0.0.1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:58967         -> 10.0.0.2:53            [dns] req, (PTR, "252.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:55984         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:51331         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:58967         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:63635         -> 10.0.0.2:53            [dns] req, (PTR, "255.255.255.255.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:51846         -> 10.0.0.2:53            [dns] req, (PTR, "250.255.255.239.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:63635         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:51846         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49692         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.f.f.1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49692         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49692         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49692         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49693         -> 10.0.0.2:53            [dns] req, (PTR, "250.255.255.239.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49693         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "4.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "5.1.d.4.7.0.1.6.5.6.b.d.d.3.0.f.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "c.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "6.1.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.0.2.0.f.f.ip6.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49694         -> 10.0.0.2:53            [dns] req, (PTR, "22.0.0.224.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, ("22.0.0.224.in-addr.arpa", PTR("igmp.mcast.net"))
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49694         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49695         -> 10.0.0.2:53            [dns] req, (PTR, "255.255.255.255.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49695         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49696         -> 10.0.0.2:53            [dns] req, (PTR, "3.f.e.9.4.5.8.2.8.6.b.b.6.2.c.7.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49696         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49697         -> 10.0.0.2:53            [dns] req, (PTR, "0.0.0.0.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49697         -> 10.0.0.2:53            [dns] req, (PTR, "14.0.0.10.in-addr.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49697         [dns] resp, []
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49697         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49698         -> 10.0.0.2:53            [dns] req, (PTR, "5.b.e.2.b.d.4.b.c.9.f.d.5.b.1.e.0.0.3.7.5.3.c.2.5.9.1.5.8.c.d.f.ip6.arpa")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:49698         [dns] resp, []
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49699         -> 10.0.0.2:53            [dns] req, (PTR, "7.0.0.10.in-addr.arpa")
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:49699         -> 10.0.0.2:53            [dns] req, (PTR, "b.c.2.8.f.9.6.4.2.4.a.8.5.f.0.e.0.0.0.0.0.0.0.0.0.0.0.0.0.8.e.f.ip6.arpa")
\end{lstlisting}

\begin{lstlisting}
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:52255         -> 10.0.0.2:53            [dns] req, (A, "45jngpxc4cgsxqxc.tor2web.org")
c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:52255         [dns] resp, ("45jngpxc4cgsxqxc.tor2web.org", A(192.36.27.5))
                                                                                                           ("45jngpxc4cgsxqxc.tor2web.org", A(185.100.85.150))
																										   00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [udp] 10.0.0.5:51166         -> 10.0.0.2:53            [dns] req, (AAAA, "45jngpxc4cgsxqxc.tor2web.org")
																										   c8:51:95:2c:35:73 -> 00:16:6f:98:80:74, [udp] 10.0.0.2:53            -> 10.0.0.5:51166         [dns] resp, ("45jngpxc4cgsxqxc.tor2web.org", AAAA(2a03:f85:8::5))
\end{lstlisting}

Possibly user checking ransom instruction on TOR hideen service.
\begin{lstlisting}
00:16:6f:98:80:74 -> c8:51:95:2c:35:73, [tcp] 10.0.0.5:49219         -> 192.36.27.5:80         [http] Request { method: "GET", uri: "/", version: "1.1", host: Some("45jngpxc4cgsxqxc.tor2web.org"), agent: Some("Mo
zilla/4.0 (compatible; MSIE 8.0; Windows NT 6.1; Trident/4.0; SLCC2; .NET CLR 2.0.50727; .NET CLR 3.5.30729; .NET CLR 3.0.30729; Media Center PC 6.0; InfoPath.2)"), referer: None, auth: None, cookies: None }
\end{lstlisting}

Random interaction between local hosts weird. 
\begin{lstlisting}
